### 2020-04-01 06b-bisimulation.tex
flat function

To simplify the query language, we first introduce a function that takes a solid link chain and returns a simple string by eliminating all the channel matching pairs leaving just one channel per each pair. This transformation is harmless, in the sense that it retains all the information in the chain, because it is applied to solid chains only. The function $\mathit{flat}$ is defined inductively as follows:
\[
\begin{array}{lcl@{\hspace{0.5cm}}lcl@{\hspace{0.5cm}}lcl@{\hspace{0.5cm}}lcl}
\mathit{flat}(\epsilon)&\defeq & \epsilon &
\mathit{flat}(\link{\silent}{\beta}) & \defeq & \beta &
\mathit{flat}(\link{\alpha}{\silent})& \defeq & \epsilon &
\mathit{flat}(\link{\alpha}{\beta}) & \defeq &\beta \\
\end{array}\]
\[
\begin{array}{lcl}
\mathit{flat}(\link{\alpha}{\beta}\upsilon)& \defeq & \beta :: \mathit{flat}(\upsilon)\\
\end{array}\\
\]
where  $::$ is the usual string concatenation operator.

@@

\begin{definition}[Biosimilarity  $ \sim_F $]
Given an assertion $F$, a \emph{biosimulation} $\mathbf{R}_F$ that respects $F$ is a binary relation over {\tt link}-calculus processes such that, if $P \mathrel{\mathbf{R}_F} Q$ then:
 \begin{itemize} 
 \item
 for any $v,P'$ such that 
 $P \xrightarrow{v} P'$ then there exist $v',Q'$ such that $Q  \xrightarrow{w} Q'$ with $v\equiv_F w$ and $P' \mathrel{\mathbf{R}_F} Q'$.
\item
 for any $w,Q'$ such that 
 $Q \xrightarrow{w} Q'$ then there exist $v,P'$ such that $P  \xrightarrow{v} P'$ with $v\equiv_F w$ and $P' \mathrel{\mathbf{R}_F} Q'$.
\end{itemize}
%\item i$Q \xrightarrow{v} Q'$ with $v \entails F$ iff $\exists v',P'$ s.t.~$v \stretcheq v'$, $P  \xrightarrow{v'} P'$ with $v \entails F$. and $P' \mathrel{\mathbf{R}_{F}} Q'$.
%\end{itemize}
We let $ \sim_F $ denote the largest  biosimulation and we say that $P$ is \emph{biosimilar} to $Q$, with respect to $F$, if $P \sim_F Q$.
\end{definition}

>>>>

%To simplify the query language, we first introduce a function that takes a solid link chain and returns a simple string by eliminating all the channel matching pairs leaving just one channel per each pair. This transformation is harmless, in the sense that it retains all the information in the chain, because it is applied to solid chains only. Below we denote by $\mathit{decs} = \{ s, \overline{s}, \widetilde{s},\widehat{s},\underline{s}~|~ s\in S\}$ the set of decorated names (without subscripts $_i$ and $_o$).
%The function $\mathit{flat}$ is defined inductively as follows:
%%\[
%%\begin{array}{lcl@{\hspace{0.5cm}}lcl@{\hspace{0.5cm}}lcl@{\hspace{0.5cm}}lcl}
%%\mathit{flat}(\epsilon)&\defeq & \epsilon &
%%\mathit{flat}(\link{\gamma}{\gamma'}) &  \defeq & \left \{ \begin{array}{cl} \epsilon & \mathrm{if } (\gamma = \beta_i \wedge \gamma = \beta_o)  \vee \gamma = \silent\\
%%\gamma' & \mathrm{otw }  \end{array} \right. &
%%%\mathit{flat}(\link{\alpha}{\silent})& \defeq & \epsilon &
%%%\mathit{flat}(\link{\alpha}{\beta}) & \defeq &\beta \\
%%\end{array}\]
%
%\[
%\mathit{flat}(\epsilon)\defeq \epsilon 
%\qquad
%\mathit{flat}(\link{\alpha}{\beta}) \defeq 
%\left \{ \begin{array}{ll} 
%\beta & \mbox{if $\beta\in \mathit{reacts}\cup\{\mathit{cxt}\}\cup\mathit{prods}$}\\
%\gamma & \mbox{if $\beta=\gamma_i$ with $\gamma\in\mathit{decs}$}\\
%\epsilon & \mbox{otherwise}  
%\end{array} \right. 
%\]
%
%\[
%\begin{array}{lcl}
%\mathit{flat}(\link{\alpha}{\beta}\upsilon)& \defeq & \mathit{flat}(\link{\alpha}{\beta}):: \mathit{flat}(\upsilon)\\
%\end{array}\\
%\]
%where  $::$ is the usual string concatenation operator.
%

@@

\begin{definition}[Biosimilarity  $ \sim_F $]
Given an assertion $F$, a \emph{biosimulation} $\mathbf{R}_F$ that respects $F$ is a binary relation over {\tt link}-calculus processes such that, if $P \mathrel{\mathbf{R}_F} Q$ then:
 \begin{itemize} 
 \item
 for any $v,P'$ such that 
 $P \xrightarrow{v} P'$ then there exist $w,Q'$ such that $Q  \xrightarrow{w} Q'$ with $v\equiv_F w$ and $P' \mathrel{\mathbf{R}_F} Q'$.
\item
 for any $w,Q'$ such that 
 $Q \xrightarrow{w} Q'$ then there exist $v,P'$ such that $P  \xrightarrow{v} P'$ with $v\equiv_F w$ and $P' \mathrel{\mathbf{R}_F} Q'$.
\end{itemize}
%\item i$Q \xrightarrow{v} Q'$ with $v \entails F$ iff $\exists v',P'$ s.t.~$v \stretcheq v'$, $P  \xrightarrow{v'} P'$ with $v \entails F$. and $P' \mathrel{\mathbf{R}_{F}} Q'$.
%\end{itemize}
We let $ \sim_F $ denote the largest  biosimulation and we say that $P$ is \emph{biosimilar} to $Q$, with respect to $F$, if $P \sim_F Q$.
\end{definition}
